Article Title

### 2013-07-30 sections/Theory.tex
Kreso's review comments.

Let $x_i \in \mathcal X, i=1\ldots,x_n$ denote a sample of consequtive observations of population activity of $p$ neurons in time bins $i$.  
The activity of each neuron is the real-valued firing rate, thus  $\mathcal X = \mathbb R^{p\times 1}$.  
We assume that observations are drawn from some true cumulative probability distribution $F: \mathcal X \mapsto R$. Then let $\hat F_n$ denote the empirical distribution function obtained from the observed sample, which itself is a random variable.
\begin{equation}
\hat F_n(x) = \frac 1 n \sum\limits_{i=1}^n \mathbf{1}(x \ge x_i)
\end{equation}
where $\mathbf 1(x \ge x_i)$ is the indicator function which equals 1 when all elements of $x$ are greater than the corresponding elements of $x_i$ and 0 otherwise.

@@

\paragraph{Variance-bias tradeoff:}
Let $\hat\Sigma_\gamma$ be a family of approximate (biased) covariance estimates indexed by $\gamma$. To evaluate each estimate, let's define the \emph{loss function} $\mathcal L : \Theta \times \Theta \mapsto \mathbb R$ such that $\mathcal L(\hat S,S)$ is minimized when $\hat S = S$.  Then \emph{excess loss} $\ell(\hat S, S) = \mathcal L(\hat S, S) - \mathcal L(S,S)$ assumes zero at the minimum.

>>>>

Let $x_i \in \mathcal X, i=1\ldots,x_n$ denote a sample of consequtive observations of population activity of $p$ neurons in time bins $i$.  
The activity of each neuron is the real-valued firing rate \TODO{Need to define rate more precisely}, thus  $\mathcal X = \mathbb R^{p\times 1}$.  
We assume that observations are drawn from some true cumulative probability distribution $F: \mathcal X \mapsto R$. Then let $\hat F_n$ denote the empirical distribution function obtained from the observed sample, which itself is a random variable.
\begin{equation}
\hat F_n(x) = \frac 1 n \sum\limits_{i=1}^n \mathbf{1}(x \ge x_i)
\end{equation}
where $\mathbf 1(x \ge x_i)$ is the indicator function which equals 1 when all elements of $x$ are greater than the corresponding elements of $x_i$ and 0 otherwise. \TODO{Are you using cumulative distributions to avoid binning?}

@@

\paragraph{Variance-bias tradeoff:}
Let $\hat\Sigma_\gamma$ be a family of approximate (biased) covariance estimates indexed by $\gamma$. To evaluate each estimate, let's define the \emph{loss function} $\mathcal L : \Theta \times \Theta \mapsto \mathbb R$ such that $\mathcal L(\hat S,S)$ is minimized when $\hat S = S$.  Then \emph{excess loss} $\ell(\hat S, S) = \mathcal L(\hat S, S) - \mathcal L(S,S)$ assumes zero at the minimum. \TODO{This is too abstract -- need to motivate with some examples maybe}
